Supplement to Automatic Matching of Bullet Lands

### 2016-01-07 imaging-supplement.Rnw
comment on study size

\hh{However, if we use all of the available comparisons to fit another random forest of 300 trees, the de-facto error rates for false positives and false negatives are again at 0. The estimated OOB error rates are 0.00024 for the false positive rate and 0.22180 for the false negative rate. The false positive rate is therefore virtually unchanged, while we see a slight improvement in the false negative rate for an overall OOB error rate of 0.3\%.}
<<allhamby, echo=FALSE, message=FALSE, warning=FALSE>>=
knowndatadir <- "app/images/Hamby252_3DX3P1of2/"
knowns <- dir(path=knowndatadir)
knowns <- gsub(".x3p", "", knowns)

>>>>

\hh{However, if we use all of the available comparisons to fit another random forest of 300 trees, the de-facto error rates for false positives and false negatives are again at 0. The estimated OOB error rates are 0.00024 for the false positive rate and 0.22180 for the false negative rate. The false positive rate is therefore virtually unchanged, while we see a slight improvement in the false negative rate for an overall OOB error rate of 0.3\%, i.e.\ an increase to twice the number of comparisons leads to a decrease of 25\% of the estimated error rate. This is yet another argument in favor of a larger database for training algorithms.}
<<allhamby, echo=FALSE, message=FALSE, warning=FALSE>>=
knowndatadir <- "app/images/Hamby252_3DX3P1of2/"
knowns <- dir(path=knowndatadir)
knowns <- gsub(".x3p", "", knowns)
